\bf Landslide: Systematic Testing in \classname \\ User Guide

### 2018-04-04 irb/landslide-guide-psu.tex
update psu guide per timmys commence:

You should have received a document titled {\em User Study Information Sheet} that describes your rights as a study
participant and our confidentiality procedures. If you are missing this, please contact me immediately. My email
address is {\tt bblum@cs.cmu.edu} and my phone number is 412-304-4294; email is preferred.
\\

@@

We encourage you to use Landslide on the Vagrant VM or the W204 cluster machines.
Landslide has not been tested with other configurations and may fail
mysteriously on your personal laptop, and we cannot promise to be of any help.

@@

			\item Use ./landslide -h to view command line options. The most important ones are {\tt -t}, max testing

@@

@@

						\item \texttt{./landslide -t 3h -p thr\_exit\_join}
						\item \texttt{./landslide -t 3h -p mutex\_test}
						\item \texttt{./landslide -t 3h -p paradise\_lost}
						\item \texttt{./landslide -t 3h -p broadcast\_test}
						\item \texttt{./landslide -t 3h -p paraguay}
						\item \texttt{./landslide -t 3h -p rwlock\_downgrade\_read\_test}
						\item \texttt{./landslide -t 12h -p thr\_exit\_join}
						\item \texttt{./landslide -t 12h -p mutex\_test}
						\item \texttt{./landslide -t 12h -p paradise\_lost}
						\item \texttt{./landslide -t 12h -p broadcast\_test}
						\item \texttt{./landslide -t 12h -p paraguay}
						\item \texttt{./landslide -t 12h -p rwlock\_downgrade\_read\_test}

@@

				\item To build your own custom test case, %for use with Landslide,
					put it in the {\tt pebsim/p2-basecode/user/progs} subdirectory %of the repository
					and edit the {\tt STUDENTTESTS} line in {\tt pebsim/p2-basecode/config-incomplete.mk}
					(note: NOT {\tt config.mk}; the setup script auto-generates that file).
					Then run {\tt ./psu-setup.sh} again.
					Refer to slide 37 of the Landslide lecture to make sure your test is ``Landslide-friendly''.

@@

				Landslide may also print some {\em data races}, even if it doesn't emit an HTML bug report. These are not necessarily bugs; please refer to slide 29 of the Landslide lecture for details about what this means.

@@

		(Remember to re-run {\tt psu-setup.sh} to make sure Landslide sees your updates.)

@@

\noindent {\bf Note on simultaneous Landslides:} Landslide does not support running multiple tests at once;
it needs to create some temporary files to annotate your code, and multiple instances of Landslide can step on each other's toes by clobbering those files.
If you want to try multiple tests at once, simply {\tt git clone} the repository again in a different directory, and run one instance of Landslide in each.
\\

>>>>

You should have received a document titled {\em User Study Information Sheet} that describes your rights as a study
participant and our confidentiality procedures. If you are missing this, please contact me immediately. My email
address is {\tt bblum@cs.cmu.edu}.
\\

@@

We encourage you to use Landslide on the Vagrant VM or the W204 cluster machines.
Landslide has not been tested with other configurations and may fail
mysteriously on other development environments, and we cannot promise to be of any help.

@@

			\item Use {\tt ./landslide -h} to view command line options. The most important ones are {\tt -t}, max testing

@@

						%	\\
						%\item \texttt{./landslide -t 3h -p thr\_exit\_join}
						%\item \texttt{./landslide -t 3h -p mutex\_test}
						%\item \texttt{./landslide -t 3h -p paradise\_lost}
						%\item \texttt{./landslide -t 3h -p broadcast\_test}
						%\item \texttt{./landslide -t 3h -p paraguay}
						%\item \texttt{./landslide -t 3h -p rwlock\_downgrade\_read\_test}

@@

						\item \texttt{./landslide -t 8h -p thr\_exit\_join}
						\item \texttt{./landslide -t 8h -p mutex\_test}
						\item \texttt{./landslide -t 8h -p paradise\_lost}
						\item \texttt{./landslide -t 8h -p broadcast\_test}
						\item \texttt{./landslide -t 8h -p paraguay}
						\item \texttt{./landslide -t 8h -p rwlock\_downgrade\_read\_test}

@@

				%\item To build your own custom test case, %for use with Landslide,
				%	put it in the {\tt pebsim/p2-basecode/user/progs} subdirectory %of the repository
				%	and edit the {\tt STUDENTTESTS} line in {\tt pebsim/p2-basecode/config-incomplete.mk}
				%	(note: NOT {\tt config.mk}; the setup script auto-generates that file).
				%	Then run {\tt ./psu-setup.sh} again.
				%	Refer to slide 37 of the Landslide lecture to make sure your test is ``Landslide-friendly''.

@@

				Landslide may also print some {\em data races},
				even if it doesn't emit an HTML bug report,
				for example as follows:
				\[
					\texttt{Found a racy access at 0x0100291e in atomic\_compare\_swap (atomic.S:42)}
				\]
				These are not necessarily bugs; please refer to slide 29 of the Landslide lecture for details about what this means.

@@

		(Remember to re-run {\tt psu-setup.sh} as in step 2 to make sure Landslide sees your updates.)

@@

\noindent {\bf Note on simultaneous Landslides:} Landslide does not support running multiple tests at once;
it needs to create some temporary files to annotate your code, and multiple instances of Landslide can step on each other's toes by clobbering those files.
%If you want to try multiple tests at once, simply {\tt git clone} the repository again in a different directory, and run one instance of Landslide in each.
\\
